Statistical paradoxes in coronavirus case-counts: selection bias, measurement error, and the COVID-19 pandemic

### 2021-09-01 write-up/covid-writeup.tex
Update MB AIR

 While the model-based estimates appear more reasonable, note that the estimate on the last week of April is 0.25\% which is a severe underestimate compared to the estimated prevalence using the stratified random sample. Caution is therefore warranted when interpreting these estimates.  Infection fatality rates are likely time-varying and may vary by other factors such as quality of healthcare.  Therefore, improvements could be made by using more accurate IFR estimates, but there is currently minimal publicly available data to do so.  Moreover, the (thankfully) low number of deaths per strata make uncertainty in these estimates quite high.  Finally, the doubly robust estimate appears similar to the IPW estimate.

>>>>

 While the model-based estimates appear more reasonable outside the summer months, note that the estimate on the last week of April is $0.30\%$ which is a severe underestimate compared to the estimated prevalence using the stratified random sample of $1.81\%$. Caution is therefore warranted when interpreting these estimates.  Infection fatality rates are likely time-varying and may vary by other factors such as quality of healthcare.  Therefore, improvements could be made by using more accurate IFR estimates, but there is currently minimal publicly available data to do so.  Moreover, the (thankfully) low number of deaths per strata make uncertainty in these estimates quite high.  Finally, the doubly robust estimate appears similar to the IPW estimate.
